---
title: 'Practice Effects on Cognitive Domain and AFQT Tests: Raw scores adjusted for
  Education and Z-scored'
author: "Jeremy Elman"
date: '`r Sys.Date()`'
output:
  pdf_document: default
  html_document:
    theme: readable
  word_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

```{r, include=F}
library(dplyr)
library(psych)
library(knitr)
library(permute)
library(boot)
```

```{r, include=F}
# Load data
allDat = read.csv("/home/jelman/netshare/K/Projects/PracticeEffects/data/CogData_TEDALL_Adj_Zscored.csv")

# Select subjects from groups of interest
subsetDat = allDat %>%
  filter(VETSAGRP=="V1V2" | VETSAGRP=="V1" | VETSAGRP=="V2AR")

# Take out V1ne subject in order to add back in later
V1neDat = allDat %>% filter(VETSAGRP=="v1ne")

# Create vector of all variable names to calculate practice effects for
testVars = c("zMR1COR","zTRL1TLOG","zTRL2TLOG","zTRL3TLOG","zTRL4TLOG","zTRL5TLOG","zCSSACC","zMTXRAW","zCVA1RAW",
             "zCVATOT","zCVSDFR","zCVLDFR","zAFQTPCT","zAFQTVOCPCT","zAFQTARPCT","zAFQTTLPCT","zAFQTBXPCT",
             "zAFQTPCTTRAN","zAFQTVOCPCTTRAN","zAFQTARPCTTRAN","zAFQTTLPCTTRAN","zAFQTBXPCTTRAN","zDSFRAW",
             "zDSBRAW","zSSPFRAW","zSSPBRAW","zLNTOT","zLMITOT","zLMDTOT","zVRITOT","zVRDTOT","zVRCTOT","zHFTOTCOR",
            "zSTRWRAW","zSTRCRAW","zSTRCWRAW","zLFFCOR","zLFACOR","zLFSCOR","zLFCOR","zCFANCOR","zCFBNCOR","zCFCOR",
            "zCSCOR","zSRTLMEANLOG","zSRTLSTDLOG","zSRTRMEANLOG","zSRTRSTDLOG","zSRTGMEANLOG","zSRTGSTDLOG",
            "zCHRTLMEANLOG","zCHRTRMEANLOG","zCHRTLSTDLOG","zCHRTRSTDLOG","zCHRTGMEANLOG","zCHRTGSTDLOG","zRSATOT")

# Create list of cognitive domains to present separately
cogVars = c("zVisSpat","zSTWKMem","zEpsMem","zAbsReason","zVerbFlu",
               "zExecTrailsSwitch","zProcSpeed","zExecCategorySwitch")

# Create list of test variables and cognitive domains
allVars = c(testVars, cogVars)

#Create list of AFQT scores to present separately
afqtVars = c("zAFQTPCT","zAFQTVOCPCT","zAFQTARPCT","zAFQTTLPCT","zAFQTBXPCT","zAFQTPCTTRAN",
            "zAFQTVOCPCTTRAN","zAFQTARPCTTRAN","zAFQTTLPCTTRAN","zAFQTBXPCTTRAN")

# Create indices of different groups
idxS1T2 = which(subsetDat$VETSAGRP=="V1V2")
idxS1T1ret = which(subsetDat$VETSAGRP=="V1V2")
idxS2T2 = which(subsetDat$VETSAGRP=="V2AR")
```

## Adjustment for Education and standardization

1. The scores have been adjusted for education by regressing the (scaled) TEDALL variable from each raw test score. 
2. VETSA 1 and VETSA 2 scores are then standardized (z-scored) using the mean and SD of VETSA 1 scores. 
3. Practice effects are calculated from these z-scores.
4. Practice effects for cognitive domains are created by averaging the practice effects from all tests within a domain.

## Calculation of practice effects  

The difference (D) between time 2 scores of longitudinal returnees (S1T2) and time 2 attrition replacements (S2T2) is the sum of attrition effects (A) and practice effects (P). The attrition effect is calculated as the difference in time 1 scores of returnees (S1T1ret) compared to the entire group (S1T1all). The practice effect is therefore the difference D minus the attrition effect.


> $D = A + P$  
> 
> *Difference score*:
> $D = S1T2 - S2T2$  
>  
> *Attrition effect*:
> $A = S1T1ret - S1T1all$  
> 
> *Practice effect*:
> $P = D - A$  


```{r, include=F}
# Define function to calculate practice effects as specified above.
calcPracticeEffect = function(dat, varName, idxS1T2, idxS2T2,idxS1T1ret){
  varV1 = varName
  varV2 = paste0(varV1, "_V2")
  varV1 = paste0(varV1,"_adj")
  varV2 = paste0(varV2,"_adj")
  # Longitudinal Subjects Time 2
  S1T2 = mean(dat[idxS1T2, varV2], na.rm=T)
  # Attrition Replacement Subjects Time 2
  S2T2 = mean(dat[idxS2T2, varV2], na.rm=T)
  # Longitudinal Returnees Time 1
  S1T1ret = mean(dat[idxS1T1ret, varV1], na.rm=T)
  # All Subjects Time 1
  S1T1all = mean(dat[, varV1], na.rm=T)
  
  # Difference score
  D = S1T2 - S2T2
  # Attrition effect
  A = S1T1ret - S1T1all
  # Practice Effect
  P = D - A
  P
}

# Define function to create composite cognitive domains 
calcCogDomains = function(testdat){
  testdat[['zVisSpat']] = mean(testdat[c("zMR1COR","zHFTOTCOR")])
  testdat[['zAbsReason']] = testdat['zMTXRAW']
  testdat[['zSTWKMem']] = mean(testdat[c("zDSFRAW","zDSBRAW","zLNTOT","zSSPFRAW",
                                              "zSSPBRAW","zRSATOT")])
  testdat[['zEpsMem']] = mean(testdat[c("zCVATOT","zCVSDFR","zCVLDFR","zLMITOT",
                                               "zLMDTOT","zVRITOT","zVRDTOT")])
  testdat[['zVerbFlu']] = mean(testdat[c("zLFCOR","zCFCOR")])
  testdat[['zProcSpeed']] = mean(testdat[c("zSTRWRAW","zSTRCRAW","zTRL2TLOG","zTRL3TLOG")])
  testdat[['zExecTrailsSwitch']] = testdat['zTRL4TLOG']
  testdat[['zExecCategorySwitch']] = testdat['zCSSACC']
  testdat
}

```


```{r, include=F}
# Calculate practice effects for all cognitive domains and tests
pracEffects = sapply(testVars, function(x) calcPracticeEffect(subsetDat, x, idxS1T2,
                                                          idxS2T2, idxS1T1ret))
pracEffects = calcCogDomains(pracEffects)
```


```{r, include=F}
### Run permutation testing to generate p-values for practice effects ###

set.seed(21)
# Set parameters for permutation testing of practice effects
N = nrow(subsetDat)                # Numer of subjects
nPerm = 10000                      # Number of permutations to run
nLong = length(idxS1T1ret)         # Number of longitudinal subjects
nAR = length(idxS2T2)              # Number of attrition replacement subjects

# Get indices of different groups
idxV1V2 = which(subsetDat$VETSAGRP=="V1V2")
idxV2AR = which(subsetDat$VETSAGRP=="V2AR")
idxV1 = which(subsetDat$VETSAGRP=="V1")

# Initialize empty matrix for permutation results
permResults = matrix(ncol=length(allVars), nrow=nPerm)
colnames(permResults) = allVars

# Run permutations and collect results into matrix
for(i in 1:nPerm){
    idxT2 = sample(c(idxV1V2, idxV2AR))
    idxT1 = sample(c(idxV1V2, idxV1))
    
    idxS1T2perm = idxT2[1:nLong]
    idxS2T2perm = idxT2[(nLong+1):(nLong+nAR)]
    idxS1T1retperm = idxT1[1:nLong]
    tmpResults = sapply(testVars, function(x) calcPracticeEffect(subsetDat, x, 
                                                      idxS1T2perm,
                                                      idxS2T2perm,
                                                      idxS1T1retperm))
    permResults[i,] = calcCogDomains(tmpResults)
}
permResults = data.frame(permResults)
# Calculate p values based on permutations and observed values
pvalsPerm = apply(permResults, 1, function(x) pracEffects > abs(x))
pvals = 1 - (rowMeans(pvalsPerm))
```

```{r, include=FALSE}
### Generate bootstrapped confidence intervals and standard error ###

bootPracticeEffect = function(data, idx){
  dat = data[idx,]
  idxV1V2boot = which(dat$VETSAGRP=="V1V2")
  idxV2ARboot = which(dat$VETSAGRP=="V2AR")
  sampResults = sapply(testVars, function(x) calcPracticeEffect(dat, x, 
                                                  idxV1V2boot,
                                                  idxV2ARboot,
                                                  idxV1V2boot))
  sampResults = calcCogDomains(sampResults)
  return(sampResults)
}

set.seed(21)
nBoot = 10000
boot.out = boot(subsetDat, statistic=bootPracticeEffect, strata=subsetDat$VETSAGRP, R=nBoot)

# # Alternative way to conduct bootstrapping
# set.seed(21)
# # Set parameters for permutation testing of practice effects
# N = nrow(subsetDat)                   # Numer of subjects
# nBoot = 1000                      # Number of boostrap resamples to run
# nLong = length(idxS1T1ret)         # Number of longitudinal subjects
# nAR = length(idxS2T2)              # Number of attrition replacement subjects
# 
# # Get indices of different groups
# idxV1V2 = which(subsetDat$VETSAGRP=="V1V2")
# idxV2AR = which(subsetDat$VETSAGRP=="V2AR")
# 
# # Initialize empty matrix for boostrap results
# bootResults = matrix(ncol=length(allVars), nrow=nBoot)
# colnames(bootResults) = allVars
# 
# # Run bootstrap resamples and collect results into matrix
# for(i in 1:nBoot){
#     idxV1V2boot = sample(idxV1V2, replace=TRUE)
#     idxV2ARboot = sample(idxV2AR, replace=TRUE)
#     bootResults[i,] = sapply(allVars, function(x) calcPracticeEffect(subsetDat, x, 
#                                                       idxV1V2boot,
#                                                       idxV2ARboot,
#                                                       idxV1V2boot))
# }
```


```{r, include=F}
### Gather results into dataframe ###

# Combine practice effects results and permutation p-values
results = data.frame("PracticeEffect" = pracEffects, SE=apply(boot.out$t, 2, sd), "P" = pvals)

# # Get indices of cognitive domains
# idxCogDomains = which(rownames(results) %in% cogDomains)

# Get indices of AFQT tests
idxAFQT = which(rownames(results) %in% afqtVars)
idxCogDomains = which(rownames(results) %in% cogVars)

#Split results into composite scores of individual tests, cognitive domains, and AFQT.
# resultsCogDomains = results[idxCogDomains,]
resultsAFQT = results[idxAFQT,]
resultsCogDomains = results[idxCogDomains,]
resultsTests = results[-c(idxAFQT,idxCogDomains),]
```

--------------------------------------

P-values for practice effects were determined through permutation testing with `r nPerm` permutations. 
Standard Errors were determined through bootstrapping with `r nBoot` resamples.



```{r, echo=F}
kable(resultsTests, digits=3, caption="Individual Tests")
```


```{r, echo=F}
kable(resultsCogDomains, digits=3, caption="Cognitive Domain Composites")
```


```{r, echo=F}
kable(resultsAFQT, digits=3, caption="AFQT Scores")
```

```{r, include=F}
# Write out practice effect results (adjustment value, estimate of precision, and p value)
write.csv(results, '/home/jelman/netshare/K/Projects/PracticeEffects/results/PracEffects_TEDALL_Zscored_Results.csv')
```



