---
title: 'Practice Effects on Cognitive Tests and AFQT Tests: 
        Adjusted for Education, raw scale score'
author: "Jeremy Elman"
date: '`r Sys.Date()`'
output:
  pdf_document: default
  html_document:
    theme: readable
  word_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

```{r, include=F}
library(dplyr)
library(psych)
library(knitr)
library(permute)
library(boot)
```

```{r, include=F}
# Load data
allDat = read.csv("~/netshare/M/PSYCH/KREMEN/Practice Effect Cognition/data/V1V2_CogData_TEDALLAdj.csv")

# Select subjects from groups of interest
subsetDat = allDat %>%
  filter(VETSAGRP=="V1V2" | VETSAGRP=="V1" | VETSAGRP=="V2AR")

# Take out V1ne subject in order to add back in later
V1neDat = allDat %>% filter(VETSAGRP=="v1ne")

# Create vector of all variable names to calculate practice effects for
testVars = c("MR1COR","TRL1TLOG","TRL2TLOG","TRL3TLOG","TRL4TLOG","TRL5TLOG","CSSACC","MTXRAW","CVA1RAW",
             "CVATOT","CVSDFR","CVLDFR","AFQTPCT","AFQTVOCPCT","AFQTARPCT","AFQTTLPCT","AFQTBXPCT",
             "AFQTPCTTRAN","AFQTVOCPCTTRAN","AFQTARPCTTRAN","AFQTTLPCTTRAN","AFQTBXPCTTRAN","DSFRAW",
             "DSBRAW","DSFMAX","SSPFRAW","SSPBRAW","LNTOT","LMITOT","LMDTOT","VRITOT","VRDTOT","VRCTOT","HFTOTCOR",
             "STRWRAW","STRCRAW","STRCWRAW","STRIT","LFFCOR","LFACOR","LFSCOR","LFCOR","CFANCOR","CFBNCOR","CFCOR",
             "CSCOR","SRTLMEANLOG","SRTLSTDLOG","SRTRMEANLOG","SRTRSTDLOG","SRTGMEANLOG","SRTGSTDLOG",
             "CHRTLMEANLOG","CHRTRMEANLOG","CHRTLSTDLOG","CHRTRSTDLOG","CHRTGMEANLOG","CHRTGSTDLOG","RSATOT",
             "AXHITRATE","AXFARATE","AXMISSRATE","BXHITRATE","BXFARATE","BXMISSRATE","CPTDPRIME")


#Create list of AFQT scores to present separately
afqtVars = c("AFQTPCT","AFQTVOCPCT","AFQTARPCT","AFQTTLPCT","AFQTBXPCT","AFQTPCTTRAN",
            "AFQTVOCPCTTRAN","AFQTARPCTTRAN","AFQTTLPCTTRAN","AFQTBXPCTTRAN")

# Create indices of different groups
idxS1T2 = which(subsetDat$VETSAGRP=="V1V2")
idxS1T1ret = which(subsetDat$VETSAGRP=="V1V2")
idxS2T2 = which(subsetDat$VETSAGRP=="V2AR")
```

## Adjustment for Education and standardization

1. The scores have been adjusted for education by regressing the (scaled) TEDALL variable from each raw test score. 
2. Practice effects are calculated from scores on the raw score scale.


## Calculation of practice effects  

The difference (D) between time 2 scores of longitudinal returnees (S1T2) and time 2 attrition replacements (S2T2) is the sum of attrition effects (A) and practice effects (P). The attrition effect is calculated as the difference in time 1 scores of returnees (S1T1ret) compared to the entire group (S1T1all). The practice effect is therefore the difference D minus the attrition effect.


> $D = A + P$  
> 
> *Difference score*:
> $D = S1T2 - S2T2$  
>  
> *Attrition effect*:
> $A = S1T1ret - S1T1all$  
> 
> *Practice effect*:
> $P = D - A$  


```{r, include=F}
# Define function to calculate practice effects as specified above.
calcPracticeEffect = function(dat, varName, idxS1T2, idxS2T2,idxS1T1ret){
  varV1 = varName
  varV2 = paste0(varV1, "_V2")
  varV1 = paste0(varV1,"_ted")
  varV2 = paste0(varV2,"_ted")
  # Longitudinal Subjects Time 2
  S1T2 = mean(dat[idxS1T2, varV2], na.rm=T)
  # Attrition Replacement Subjects Time 2
  S2T2 = mean(dat[idxS2T2, varV2], na.rm=T)
  # Longitudinal Returnees Time 1
  S1T1ret = mean(dat[idxS1T1ret, varV1], na.rm=T)
  # All Subjects Time 1
  S1T1all = mean(dat[, varV1], na.rm=T)
  
  # Difference score
  D = S1T2 - S2T2
  # Attrition effect
  A = S1T1ret - S1T1all
  # Practice Effect
  P = D - A
  P
}

```


```{r, include=F}
# Calculate practice effects for all tests
pracEffects = sapply(testVars, function(x) calcPracticeEffect(subsetDat, x, idxS1T2,
                                                          idxS2T2, idxS1T1ret))
```


```{r, include=F}
### Run permutation testing to generate p-values for practice effects ###

set.seed(21)
# Set parameters for permutation testing of practice effects
N = nrow(subsetDat)                # Numer of subjects
nPerm = 100                     # Number of permutations to run
nLong = length(idxS1T1ret)         # Number of longitudinal subjects
nAR = length(idxS2T2)              # Number of attrition replacement subjects

# Get indices of different groups
idxV1V2 = which(subsetDat$VETSAGRP=="V1V2")
idxV2AR = which(subsetDat$VETSAGRP=="V2AR")
idxV1 = which(subsetDat$VETSAGRP=="V1")

# Initialize empty matrix for permutation results
permResults = matrix(ncol=length(testVars), nrow=nPerm)
colnames(permResults) = testVars

# Run permutations and collect results into matrix
for(i in 1:nPerm){
    idxT2 = sample(c(idxV1V2, idxV2AR))
    idxT1 = sample(c(idxV1V2, idxV1))
    
    idxS1T2perm = idxT2[1:nLong]
    idxS2T2perm = idxT2[(nLong+1):(nLong+nAR)]
    idxS1T1retperm = idxT1[1:nLong]
    tmpResults = sapply(testVars, function(x) calcPracticeEffect(subsetDat, x, 
                                                      idxS1T2perm,
                                                      idxS2T2perm,
                                                      idxS1T1retperm))
    permResults[i,] = tmpResults
}
permResults = data.frame(permResults)
# Calculate p values based on permutations and observed values
pvalsPerm = apply(permResults, 1, function(x) abs(x) >= abs(pracEffects))
pvals = rowMeans(pvalsPerm)
```

```{r, include=FALSE}
### Generate bootstrapped confidence intervals and standard error ###

bootPracticeEffect = function(data, idx){
  dat = data[idx,]
  idxV1V2boot = which(dat$VETSAGRP=="V1V2")
  idxV2ARboot = which(dat$VETSAGRP=="V2AR")
  sampResults = sapply(testVars, function(x) calcPracticeEffect(dat, x, 
                                                  idxV1V2boot,
                                                  idxV2ARboot,
                                                  idxV1V2boot))
  return(sampResults)
}

set.seed(21)
nBoot = 10000
boot.out = boot(subsetDat, statistic=bootPracticeEffect, strata=subsetDat$VETSAGRP, R=nBoot)

# # Alternative way to conduct bootstrapping
# set.seed(21)
# # Set parameters for permutation testing of practice effects
# N = nrow(subsetDat)                   # Numer of subjects
# nBoot = 1000                      # Number of boostrap resamples to run
# nLong = length(idxS1T1ret)         # Number of longitudinal subjects
# nAR = length(idxS2T2)              # Number of attrition replacement subjects
# 
# # Get indices of different groups
# idxV1V2 = which(subsetDat$VETSAGRP=="V1V2")
# idxV2AR = which(subsetDat$VETSAGRP=="V2AR")
# 
# # Initialize empty matrix for boostrap results
# bootResults = matrix(ncol=length(testVars), nrow=nBoot)
# colnames(bootResults) = testVars
# 
# # Run bootstrap resamples and collect results into matrix
# for(i in 1:nBoot){
#     idxV1V2boot = sample(idxV1V2, replace=TRUE)
#     idxV2ARboot = sample(idxV2AR, replace=TRUE)
#     bootResults[i,] = sapply(testVars, function(x) calcPracticeEffect(subsetDat, x, 
#                                                       idxV1V2boot,
#                                                       idxV2ARboot,
#                                                       idxV1V2boot))
# }
```


```{r, include=F}
### Gather results into dataframe ###

# Combine practice effects results and permutation p-values
results = data.frame("PracticeEffect" = pracEffects, SE=apply(boot.out$t, 2, sd), "P" = pvals)

# Get indices of AFQT tests
idxAFQT = which(rownames(results) %in% afqtVars)

#Split results into composite scores of individual tests and AFQT.
resultsAFQT = results[idxAFQT,]
resultsTests = results[-c(idxAFQT),]
```

--------------------------------------

P-values for practice effects were determined through permutation testing with `r nPerm` permutations. 
Standard Errors were determined through bootstrapping with `r nBoot` resamples.


```{r, echo=F}
kable(resultsTests, digits=3, caption="Individual Tests")
```


```{r, echo=F}
kable(resultsAFQT, digits=3, caption="AFQT Scores")
```

```{r, include=F}
# Write out practice effect results (adjustment value, estimate of precision, and p value)
write.csv(results, '~/netshare/M/PSYCH/KREMEN/Practice Effect Cognition/results/PracEffectValues_TEDALLAdj.csv')
```



