---
title: "Practice Effects on Cognitive Domain and AFQT Tests: Unadjusted scores"
author: "Jeremy Elman"
date: '`r Sys.Date()`'
output:
  pdf_document:
    latex_engine: xelatex
  html_document:
    theme: readable
  word_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

```{r, include=F}
library(dplyr)
library(psych)
library(knitr)
library(permute)
```

```{r, include=F}
# Load demographic data
demoData = read.csv("K:/data/VETSA_demo_vars.csv", stringsAsFactors = F)
# Load VETSA 1 Cognitive Domain data
vetsa1CogDomains = read.csv("K:/Projects/PracticeEffects/data/V1_CognitiveDomains.csv", stringsAsFactors = F)
# Rename zrsatotrevtran variable in V1 to match variable name in V2
vetsa1CogDomains = dplyr::rename(vetsa1CogDomains, zrsatottran=zrsatotrevtran)
# Load VETSA 2 Cognitive Domain data
vetsa2CogDomains = read.csv("K:/Projects/PracticeEffects/data/V2_CognitiveDomains.csv", stringsAsFactors = F)
# Load VETSA 1 AFQT data
vetsa1afqt = read.csv("K:/Projects/PracticeEffects/data/V1_AFQTscores_Zscored.csv",
                      stringsAsFactors = F)
# Load VETSA 2 AFQT data
vetsa2afqt = read.csv("K:/Projects/PracticeEffects/data/V2_AFQTscores_Zscored.csv",
                      stringsAsFactors = F)

# Join demographic data with VETSA1 & VETSA2 datasets
allDat = demoData %>%
  left_join(vetsa1CogDomains, by="vetsaid") %>% 
  left_join(vetsa2CogDomains, by="vetsaid") %>%
  left_join(vetsa1afqt, by="vetsaid") %>%
  left_join(vetsa2afqt, by="vetsaid")

# Select subjects from groups of interest
allDat = allDat %>%
  filter(VETSAGRP=="V1V2" | VETSAGRP=="V1" | VETSAGRP=="V2AR")

```

## Calculation of practice effects  

The difference (D) between time 2 scores of longitudinal returnees (S1T2) and time 2 attrition replacements (S2T2) is the sum of attrition effects (A) and practice effects (P). The attrition effect is calculated as the difference in time 1 scores of returnees (S1T1ret) compared to the entire group (S1T1all). The practice effect is therefore the difference D minus the attrition effect.

> $D = A + P$  
> 
> *Difference score*:
> $D = S1T2 - S2T2$  
>  
> *Attrition effect*:
> $A = S1T1ret - S1T1all$  
> 
> *Practice effect*:
> $P = D - A$  


```{r, include=F}
calcPracticeEffect = function(dat, varName, idxS1T2, idxS2T2,idxS1T1ret){
  varV1 = varName
  varV2 = paste0(varV1, "_v2")
  
  # Longitudinal Subjects Time 2
  S1T2 = mean(dat[idxS1T2, varV2], na.rm=T)
  # Attrition Replacement Subjects Time 2
  S2T2 = mean(dat[idxS2T2, varV2], na.rm=T)
  # Longitudinal Returnees Time 1
  S1T1ret = mean(dat[idxS1T1ret, varV1], na.rm=T)
  # All Subjects Time 1
  S1T1all = mean(dat[, varV1], na.rm=T)
  
  # Difference score
  D = S1T2 - S2T2
  # Attrition effect
  A = S1T1ret - S1T1all
  # Practice Effect
  P = D - A
  P
}
```


```{r, include=F}
# Create vector of all variable names to calculate practice effects for
allVars = c("zVisSpat","zMR1COR","zHFTOTCOR","zSTWKMem","zdsfraw","zdsbraw",
            "zlntot","zsspfraw","zsspbraw","zrsatottran","zEpsMem","zcvatot",
            "zcvsdfr","zcvldfr","zlmitot","zlmdtot","zvritot","zvrdtot",
            "zAbsReason","zMTXTRAN","zVerbFlu","zlfcor","zcfcor",
            "zExecTrailsSwitch","ztrl4adjtran","zProcSpeed","zstrwraw",
            "zstrcraw","ztrl2tran","ztrl3tran","zExecCategorySwitch",
            "zCSSACCADJ","zExecInhibit","zstrit","zafqtpcttran","zafqtvocpcttran",
            "zafqtarpcttran","zafqttlpcttran","zafqtbxpcttran")
# Create list of cognitive domains to present separately
cogDomains = c("zVisSpat","zSTWKMem","zEpsMem","zAbsReason","zVerbFlu",
               "zExecTrailsSwitch","zProcSpeed","zExecCategorySwitch",
               "zExecInhibit")
#Create list of AFQT scores to present separately
afqtVars = c("zafqtpcttran","zafqtvocpcttran","zafqtarpcttran","zafqttlpcttran",
             "zafqtbxpcttran")

# Create indices of different groups
idxS1T2 = which(allDat$VETSAGRP=="V1V2")
idxS1T1ret = which(allDat$VETSAGRP=="V1V2")
idxS2T2 = which(allDat$VETSAGRP=="V2AR")
# Calculate practice effects for all cognitive domains and tests
pracEffects = sapply(allVars, function(x) calcPracticeEffect(allDat, x, idxS1T2,
                                                          idxS2T2, idxS1T1ret))

```

```{r, include=F}
set.seed(21)
# Set parameters for permutation testing of practice effects
N = nrow(allDat)                   # Numer of subjects
nPerm = 10000                      # Number of permutations to run
nLong = length(idxS1T1ret)         # Number of longitudinal subjects
nAR = length(idxS2T2)              # Number of attrition replacement subjects

# Get indices of different groups
idxV1V2 = which(allDat$VETSAGRP=="V1V2")
idxV2AR = which(allDat$VETSAGRP=="V2AR")
idxV1 = which(allDat$VETSAGRP=="V1")

# Initialize empty matrix for permutation results
permResults = matrix(ncol=length(allVars), nrow=nPerm)
colnames(permResults) = allVars

# Run permutations and collect results into matrix
for(i in 1:nPerm){
    idxT2 = sample(c(idxV1V2, idxV2AR))
    idxT1 = sample(c(idxV1V2, idxV1))
    
    idxS1T2perm = idxT2[1:nLong]
    idxS2T2perm = idxT2[(nLong+1):(nLong+nAR)]
    idxS1T1retperm = idxT1[1:nLong]
    permResults[i,] = sapply(allVars, function(x) calcPracticeEffect(allDat, x, 
                                                      idxS1T2perm,
                                                      idxS2T2perm,
                                                      idxS1T1retperm))
}
permResults = data.frame(permResults)
# Calculate p values based on permutations and observed values
pvalsPerm = apply(permResults, 1, function(x) pracEffects > abs(x))
pvals = 1 - (rowMeans(pvalsPerm))

# Combine practice effects results and permutation p-values
results = data.frame("PracticeEffect" = pracEffects, "P" = pvals)

# Get indices of cognitive domains
idxCogDomains = which(rownames(results) %in% cogDomains)
# Get indices of AFQT tests
idxAFQT = which(rownames(results) %in% afqtVars)

#Split results into composite scores of cognitive domains and individual tests
resultsCogDomains = results[idxCogDomains,]
resultsAFQT = results[idxAFQT,]
resultsTests = results[-c(idxCogDomains,idxAFQT),]
```

--------------------------------------

P-values for practice effects were determined through permutation testing with `r nPerm` permutations. 


```{r, echo=F}
kable(resultsTests, digits=3, caption="Cognitive Domain Individual Tests")
```


```{r, echo=F}
kable(resultsCogDomains, digits=3, caption="Cognitive Domain Composites")
```


```{r, echo=F}
kable(resultsAFQT, digits=3, caption="AFQT Scores")
```

```{r, echo=F}
# par(mfrow=c(ceiling(length(vars)/3),3))
# 
# hist(permResults[[x]], breaks=20)
# abline(v=quantile(permResults[[x]], c(.025, .975)), lty=2)
# abline(v=pracEffects[[x]], col='red', lty=2)
```


