---
title: "Group Comparisons for Practice Effects"
author: "Jeremy Elman"
date: '`r Sys.Date()`'
output:
  html_document:
    theme: readable
  pdf_document: default
  word_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

Group comparisons of longitudinal follow-up subjects (V1V2), attrition replacement subjects (V2AR), and drop-out subjects (V1) are listed below.  

For variables that are recorded at each wave:  
V1V2 vs. V1 comparisons use VETSA 1 data  
V1V2 vs V2AR comparisons use VETSA 2 data  
V1 vs. V2AR comparisons use VETSA1 and VETSA2 data, respectively  

```{r, include=F}
# Load libraries
library(knitr)
library(sjmisc)
library(dplyr)
library(sjPlot)

# Load in VETSA 1 data
vetsa1Dat = read_sas("/home/jelman/netshare/K/data/VETSA1_Aug2014/vetsa1merged_25aug2015_nomiss.sas7bdat")

# Select columns of interest and rename when necessary to be consistent across wave
vetsa1Dat = vetsa1Dat %>%
  dplyr::select(vetsaid,case,afqtpcttran,cesd=dep05,HYPTYN,PRVDYN,DIABYN,
         INCOME=E6,ASTHYN,BRONYN,EMPHYN,SAPNYN,ANGIYN,HATTYN,HRTFYN,THRMYN,
         GASTYN,ULCRYN,IBSYN,PANCYN,HEPAYN,HEPBYN,HEPCYN,ULCOYN,OTHYYN,UNDYYN,
         OARTYN,GOUTYN,RARTYN,GLAUYN,PTSDYN,MIGRYN,SEIZYN,STROYN,AAADYN,DEPRYN,
         ANXDYN,DADDYN,CANCYN)


# Load in VETSA 2 data
vetsa2Dat = read_sas('/home/jelman/netshare/K/data/VETSA2_April2015/vetsa2merged_1dec2015_edits.sas7bdat')
# Strip "v2" parts of variable names for easier selection
names(vetsa2Dat) = gsub("_?[Vv]2$", "", names(vetsa2Dat))

# Select columns of interest and rename when necessary to be consistent across wave
vetsa2Dat = vetsa2Dat %>%
  dplyr::select(vetsaid,case,afqtpcttran,cesd=CESdep,HYPTYN,PRVDYN,DIABYN,
         INCOME=E5,ASTHYN,BRONYN,EMPHYN,SAPNYN,ANGIYN,HATTYN,HRTFYN,THRMYN,
         GASTYN,ULCRYN,IBSYN,PANCYN,HEPAYN,HEPBYN,HEPCYN,ULCOYN,OTHYYN,UNDYYN,
         OARTYN,GOUTYN,RARTYN,GLAUYN,PTSDYN,MIGRYN,SEIZYN,STROYN,AAADYN,DEPRYN,
         ANXDYN,DADDYN,CANCYN) 


#  Load in administrative data
vetsaAdminDat = read.csv("/home/jelman/netshare/K/data/VETSA_Demographics/VETSA_demo_vars.csv", stringsAsFactors = F)
adminCols = c("vetsaid","apoe2014","nas201tran","ETHNALL","RACEALL","TEDALL",
              "AGE_IN","AGE_FU1","VETSAGRP","twin","zygos")
vetsaAdminDat = dplyr::select(vetsaAdminDat, one_of(adminCols))

# Join admin data with V1 and V2 datasets
vetsa1AllDat = vetsaAdminDat %>% 
  right_join(vetsa1Dat, by="vetsaid")
vetsa2AllDat = vetsaAdminDat %>% 
  right_join(vetsa2Dat, by="vetsaid")

# Filter for subjects of interest
vetsa1AllDat = subset(vetsa1AllDat, (VETSAGRP=="V1" | VETSAGRP=="V1V2"))
vetsa2AllDat = subset(vetsa2AllDat, (VETSAGRP=="V1V2" | VETSAGRP=="V2AR"))

# Combine V1 dropout subjects with V2 Attrition replacement subjects
vetsa1ARAllDat =  union(vetsa1AllDat[vetsa1AllDat$VETSAGRP=="V1",],
                        vetsa2AllDat[vetsa2AllDat$VETSAGRP=="V2AR",]) 

# Create factor of VETSA group
vetsa1AllDat$VETSAGRP = factor(vetsa1AllDat$VETSAGRP)
vetsa2AllDat$VETSAGRP = factor(vetsa2AllDat$VETSAGRP)
vetsa1ARAllDat$VETSAGRP = factor(vetsa1ARAllDat$VETSAGRP)
```


<br/>

**Education**  
```{r, echo=F}
# Education
t.test(TEDALL ~ VETSAGRP, data=vetsa1AllDat)
t.test(TEDALL ~ VETSAGRP, data=vetsa2AllDat)
t.test(TEDALL ~ VETSAGRP, data=vetsa1ARAllDat)
```
<br/>

**AFQT**  
```{r, echo=F}
# AFQT
t.test(afqtpcttran ~ VETSAGRP, data=vetsa1AllDat)
t.test(afqtpcttran ~ VETSAGRP, data=vetsa2AllDat)
t.test(afqtpcttran ~ VETSAGRP, data=vetsa1ARAllDat)
```
<br/>

**Age 20 AFQT**  
```{r, echo=F}
# Age 20 AFQT
t.test(nas201tran ~ VETSAGRP, data=vetsa1AllDat)
t.test(nas201tran ~ VETSAGRP, data=vetsa2AllDat)
t.test(nas201tran ~ VETSAGRP, data=vetsa1ARAllDat)
```
<br/>

**Depression**  
```{r, echo=F}
# Depression
t.test(cesd ~ VETSAGRP, data=vetsa1AllDat)
t.test(cesd ~ VETSAGRP, data=vetsa2AllDat)
t.test(cesd ~ VETSAGRP, data=vetsa1ARAllDat)
```
<br/>

**Income**  
```{r, echo=F}
# Depression
t.test(INCOME ~ VETSAGRP, data=vetsa1AllDat)
t.test(INCOME ~ VETSAGRP, data=vetsa2AllDat)
t.test(INCOME ~ VETSAGRP, data=vetsa1ARAllDat)
```

**Age**  
```{r, echo=F}
# Education
t.test(AGE_IN ~ VETSAGRP, data=vetsa1AllDat)
t.test(AGE_FU1 ~ VETSAGRP, data=vetsa2AllDat)

```

```{r}
data(efc)
efc.labels <- get_labels(efc)
```


**Ethnicity**  
`r sjt.xtab(vetsa1AllDat$ETHNALL, vetsa1AllDat$VETSAGRP, var.labels=c("Ethnicity","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$ETHNALL, vetsa2AllDat$VETSAGRP, var.labels=c("Ethnicity","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$ETHNALL, vetsa1ARAllDat$VETSAGRP, var.labels=c("Ethnicity","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Race**  
`r sjt.xtab(vetsa1AllDat$RACEALL, vetsa1AllDat$VETSAGRP,  var.labels=c("Race","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$RACEALL, vetsa2AllDat$VETSAGRP, var.labels=c("Race","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$RACEALL, vetsa1ARAllDat$VETSAGRP, var.labels=c("Race","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**APOE 4**  
0=No, 1=Yes
`r sjt.xtab(vetsa1AllDat$apoe4, vetsa1AllDat$VETSAGRP, var.labels=c("APOE 4","VETSA 1 Group"),no.output=TRUE)$knitr`
<br/>
`r sjt.xtab(vetsa2AllDat$apoe4, vetsa2AllDat$VETSAGRP, var.labels=c("APOE 4","VETSA 2 Group"),no.output=TRUE)$knitr`
<br/>
`r sjt.xtab(vetsa1ARAllDat$apoe4, vetsa1ARAllDat$VETSAGRP, var.labels=c("APOE 4","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>
    
**Hypertension**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$HYPTYN, vetsa1AllDat$VETSAGRP, var.labels=c("Hypertension","VETSA 1 Group"),no.output=TRUE)$knitr`
<br/> 
`r sjt.xtab(vetsa2AllDat$HYPTYN, vetsa2AllDat$VETSAGRP, var.labels=c("Hypertension","VETSA 2 Group"),no.output=TRUE)$knitr`
<br/>
`r sjt.xtab(vetsa1ARAllDat$HYPTYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Hypertension","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Depression**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$DEPRYN, vetsa1AllDat$VETSAGRP, var.labels=c("Depression","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$DEPRYN, vetsa2AllDat$VETSAGRP, var.labels=c("Depression","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$DEPRYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Depression","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**PTSD**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$PTSDYN, vetsa1AllDat$VETSAGRP, var.labels=c("PTSD","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$PTSDYN, vetsa2AllDat$VETSAGRP, var.labels=c("PTSD","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$PTSDYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("PTSD","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Stroke**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$STROYN, vetsa1AllDat$VETSAGRP, var.labels=c("Stroke","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$STROYN, vetsa2AllDat$VETSAGRP, var.labels=c("Stroke","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$STROYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Stroke","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

```{r, include=FALSE}
#Save out datasets used for analysis
write.csv(vetsa1AllDat, "/home/jelman/netshare/K/Projects/PracticeEffects/data/GroupComparisons_V1_V1V2.csv")
write.csv(vetsa2AllDat, "/home/jelman/netshare/K/Projects/PracticeEffects/data/GroupComparisons_V1V2_V2AR.csv")
write.csv(vetsa1ARAllDat, "/home/jelman/netshare/K/Projects/PracticeEffects/data/GroupComparisons_V1_V2AR.csv")
```