---
title: "Group Comparisons for Practice Effects"
author: "Jeremy Elman"
date: '`r Sys.Date()`'
output:
  html_document:
    theme: readable
  word_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

Group comparisons of longitudinal follow-up subjects (V1V2), attrition replacement subjects (V2AR), and drop-out subjects (V1) are listed below.  

For variables that are recorded at each wave:  
V1V2 vs. V1 comparisons use VETSA 1 data  
V1V2 vs V2AR comparisons use VETSA 2 data  
V1 vs. V2AR comparisons use VETSA1 and VETSA2 data, respectively  

```{r, include=F}
# Load libraries
library(knitr)
library(sjmisc)
library(dplyr)
library(sjPlot)

# Load in VETSA 1 data
vetsa1Dat = read_sas("/home/jelman/netshare/K/data/VETSA1_Aug2014/vetsa1merged_25aug2015_nomiss.sas7bdat")

# Select columns of interest and rename when necessary to be consistent across wave
vetsa1Dat = vetsa1Dat %>%
  dplyr::select(vetsaid,case,afqtpcttran,cesd=dep05,HYPTYN,PRVDYN,DIABYN,
         INCOME=E6,ASTHYN,BRONYN,EMPHYN,SAPNYN,ANGIYN,HATTYN,HRTFYN,THRMYN,
         GASTYN,ULCRYN,IBSYN,PANCYN,HEPAYN,HEPBYN,HEPCYN,ULCOYN,OTHYYN,UNDYYN,
         OARTYN,GOUTYN,RARTYN,GLAUYN,PTSDYN,MIGRYN,SEIZYN,STROYN,AAADYN,DEPRYN,
         ANXDYN,DADDYN,CANCYN)


# Load in VETSA 2 data
vetsa2Dat = read_sas('/home/jelman/netshare/K/data/VETSA2_April2015/vetsa2merged_1dec2015_edits.sas7bdat')
# Strip "v2" parts of variable names for easier selection
names(vetsa2Dat) = gsub("_?[Vv]2$", "", names(vetsa2Dat))

# Select columns of interest and rename when necessary to be consistent across wave
vetsa2Dat = vetsa2Dat %>%
  dplyr::select(vetsaid,case,afqtpcttran,cesd=CESdep,HYPTYN,PRVDYN,DIABYN,
         INCOME=E5,ASTHYN,BRONYN,EMPHYN,SAPNYN,ANGIYN,HATTYN,HRTFYN,THRMYN,
         GASTYN,ULCRYN,IBSYN,PANCYN,HEPAYN,HEPBYN,HEPCYN,ULCOYN,OTHYYN,UNDYYN,
         OARTYN,GOUTYN,RARTYN,GLAUYN,PTSDYN,MIGRYN,SEIZYN,STROYN,AAADYN,DEPRYN,
         ANXDYN,DADDYN,CANCYN) 


#  Load in administrative data
vetsaAdminDat = read.csv("/home/jelman/netshare/K/data/VETSA_demo_vars.csv", stringsAsFactors = F)
adminCols = c("vetsaid","apoe2014","nas201tran","ETHNALL","RACEALL","TEDALL",
              "AGE_IN","AGE_FU1","VETSAGRP","twin","zygos")
vetsaAdminDat = dplyr::select(vetsaAdminDat, one_of(adminCols))

# Join admin data with V1 and V2 datasets
vetsa1AllDat = vetsaAdminDat %>% 
  right_join(vetsa1Dat, by="vetsaid")
vetsa2AllDat = vetsaAdminDat %>% 
  right_join(vetsa2Dat, by="vetsaid")

# Filter for subjects of interest
vetsa1AllDat = subset(vetsa1AllDat, (VETSAGRP=="V1" | VETSAGRP=="V1V2"))
vetsa2AllDat = subset(vetsa2AllDat, (VETSAGRP=="V1V2" | VETSAGRP=="V2AR"))

# Combine V1 dropout subjects with V2 Attrition replacement subjects
vetsa1ARAllDat =  union(vetsa1AllDat[vetsa1AllDat$VETSAGRP=="V1",],
                        vetsa2AllDat[vetsa2AllDat$VETSAGRP=="V2AR",]) 

# Create factor of VETSA group
vetsa1AllDat$VETSAGRP = factor(vetsa1AllDat$VETSAGRP)
vetsa2AllDat$VETSAGRP = factor(vetsa2AllDat$VETSAGRP)
vetsa1ARAllDat$VETSAGRP = factor(vetsa1ARAllDat$VETSAGRP)
```


**Ethnicity**  
`r sjt.xtab(vetsa1AllDat$ETHNALL, vetsa1AllDat$VETSAGRP, var.labels=c("Ethnicity","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$ETHNALL, vetsa2AllDat$VETSAGRP, var.labels=c("Ethnicity","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$ETHNALL, vetsa1ARAllDat$VETSAGRP, var.labels=c("Ethnicity","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Race**  
`r sjt.xtab(vetsa1AllDat$RACEALL, vetsa1AllDat$VETSAGRP,  var.labels=c("Race","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$RACEALL, vetsa2AllDat$VETSAGRP, var.labels=c("Race","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$RACEALL, vetsa1ARAllDat$VETSAGRP, var.labels=c("Race","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>


**APOE 4**  
0=No, 1=Yes
`r sjt.xtab(vetsa1AllDat$apoe4, vetsa1AllDat$VETSAGRP, var.labels=c("APOE 4","VETSA 1 Group"),no.output=TRUE)$knitr`
<br/>
`r sjt.xtab(vetsa2AllDat$apoe4, vetsa2AllDat$VETSAGRP, var.labels=c("APOE 4","VETSA 2 Group"),no.output=TRUE)$knitr`
<br/>
`r sjt.xtab(vetsa1ARAllDat$apoe4, vetsa1ARAllDat$VETSAGRP, var.labels=c("APOE 4","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>
    
**Hypertension**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$HYPTYN, vetsa1AllDat$VETSAGRP, var.labels=c("Hypertension","VETSA 1 Group"),no.output=TRUE)$knitr`
<br/> 
`r sjt.xtab(vetsa2AllDat$HYPTYN, vetsa2AllDat$VETSAGRP, var.labels=c("Hypertension","VETSA 2 Group"),no.output=TRUE)$knitr`
<br/>
`r sjt.xtab(vetsa1ARAllDat$HYPTYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Hypertension","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Peripheral Vascular Disease**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$PRVDYN, vetsa1AllDat$VETSAGRP, var.labels=c("Peripheral Vascular Disease","VETSA 1 Group"),no.output=TRUE)$knitr`
<br/> 
`r sjt.xtab(vetsa2AllDat$PRVDYN, vetsa2AllDat$VETSAGRP, var.labels=c("Peripheral Vascular Disease","VETSA 2 Group"),no.output=TRUE)$knitr`
<br/>
`r sjt.xtab(vetsa1ARAllDat$PRVDYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Peripheral Vascular Disease","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Diabetes**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$DIABYN, vetsa1AllDat$VETSAGRP, var.labels=c("Diabetes","VETSA 1 Group"),no.output=TRUE)$knitr`
<br/>
`r sjt.xtab(vetsa2AllDat$DIABYN, vetsa2AllDat$VETSAGRP, var.labels=c("Diabetes","VETSA 2 Group"),no.output=TRUE)$knitr`
<br/>
`r sjt.xtab(vetsa1ARAllDat$DIABYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Diabetes","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Asthma**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$ASTHYN, vetsa1AllDat$VETSAGRP, var.labels=c("Asthma","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$ASTHYN, vetsa2AllDat$VETSAGRP, var.labels=c("Asthma","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$ASTHYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Asthma","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Chronic Bronchitis**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$BRONYN, vetsa1AllDat$VETSAGRP, var.labels=c("Chronic Bronchitis","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$BRONYN, vetsa2AllDat$VETSAGRP, var.labels=c("Chronic Bronchitis","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$BRONYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Chronic Bronchitis","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Emphysema**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$EMPHYN, vetsa1AllDat$VETSAGRP, var.labels=c("Emphysema","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$EMPHYN, vetsa2AllDat$VETSAGRP, var.labels=c("Emphysema","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$EMPHYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Emphysema","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Sleep Apnea**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$SAPNYN, vetsa1AllDat$VETSAGRP, var.labels=c("Sleep Apnea","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$SAPNYN, vetsa2AllDat$VETSAGRP, var.labels=c("Sleep Apnea","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$SAPNYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Sleep Apnea","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Angina**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$ANGIYN, vetsa1AllDat$VETSAGRP, var.labels=c("Angina","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$ANGIYN, vetsa2AllDat$VETSAGRP, var.labels=c("Angina","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$ANGIYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Angina","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Heart Attack**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$HATTYN, vetsa1AllDat$VETSAGRP, var.labels=c("Heart Attack","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$HATTYN, vetsa2AllDat$VETSAGRP, var.labels=c("Heart Attack","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$HATTYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Heart Attack","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Heart Failure**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$HRTFYN, vetsa1AllDat$VETSAGRP, var.labels=c("Heart Failure","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$HRTFYN, vetsa2AllDat$VETSAGRP, var.labels=c("Heart Failure","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$HRTFYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Heart Failure","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Thombophlebitis**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$THRMYN, vetsa1AllDat$VETSAGRP, var.labels=c("Thombophlebitis","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$THRMYN, vetsa2AllDat$VETSAGRP, var.labels=c("Thombophlebitis","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$THRMYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Thombophlebitis","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Gastritis**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$GASTYN, vetsa1AllDat$VETSAGRP, var.labels=c("Gastritis","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$GASTYN, vetsa2AllDat$VETSAGRP, var.labels=c("Gastritis","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$GASTYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Gastritis","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Stomach Ulcer**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$ULCRYN, vetsa1AllDat$VETSAGRP, var.labels=c("Stomach Ulcer","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$ULCRYN, vetsa2AllDat$VETSAGRP, var.labels=c("Stomach Ulcer","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$ULCRYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Stomach Ulcer","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Irritable Bowel Syndrome**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$IBSYN, vetsa1AllDat$VETSAGRP, var.labels=c("Irritable Bowel Syndrome","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$IBSYN, vetsa2AllDat$VETSAGRP, var.labels=c("Irritable Bowel Syndrome","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$IBSYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Irritable Bowel Syndrome","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Pancreatitis**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$PANCYN, vetsa1AllDat$VETSAGRP, var.labels=c("Pancreatitis","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$PANCYN, vetsa2AllDat$VETSAGRP, var.labels=c("Pancreatitis","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$PANCYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Pancreatitis","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Hepatitis A**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$HEPAYN, vetsa1AllDat$VETSAGRP, var.labels=c("Hepatitis A","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$HEPAYN, vetsa2AllDat$VETSAGRP, var.labels=c("Hepatitis A","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$HEPAYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Hepatitis A","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Hepatitis B**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$HEPBYN, vetsa1AllDat$VETSAGRP, var.labels=c("Hepatitis B","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$HEPBYN, vetsa2AllDat$VETSAGRP, var.labels=c("Hepatitis B","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$HEPBYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Hepatitis B","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Hepatitis C**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$HEPCYN, vetsa1AllDat$VETSAGRP, var.labels=c("Hepatitis C","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$HEPCYN, vetsa2AllDat$VETSAGRP, var.labels=c("Hepatitis C","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$HEPCYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Hepatitis C","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Ulcerative Colitis**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$ULCOYN, vetsa1AllDat$VETSAGRP, var.labels=c("Ulcerative Colitis","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$ULCOYN, vetsa2AllDat$VETSAGRP, var.labels=c("Ulcerative Colitis","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$ULCOYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Ulcerative Colitis","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Overactive Thyroid**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$OTHYYN, vetsa1AllDat$VETSAGRP, var.labels=c("Overactive Thyroid","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$OTHYYN, vetsa2AllDat$VETSAGRP, var.labels=c("Overactive Thyroid","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$OTHYYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Overactive Thyroid","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Underactive Thyroid**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$UNDYYN, vetsa1AllDat$VETSAGRP, var.labels=c("Underactive Thyroid","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$UNDYYN, vetsa2AllDat$VETSAGRP, var.labels=c("Underactive Thyroid","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$UNDYYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Underactive Thyroid","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Osteoarthritis**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$OARTYN, vetsa1AllDat$VETSAGRP, var.labels=c("Osteoarthritis","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$OARTYN, vetsa2AllDat$VETSAGRP, var.labels=c("Osteoarthritis","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$OARTYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Osteoarthritis","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Gout**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$GOUTYN, vetsa1AllDat$VETSAGRP, var.labels=c("Gout","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$GOUTYN, vetsa2AllDat$VETSAGRP, var.labels=c("Gout","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$GOUTYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Gout","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Rheumatoid Arthritis**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$RARTYN, vetsa1AllDat$VETSAGRP, var.labels=c("Rheumatoid Arthritis","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$RARTYN, vetsa2AllDat$VETSAGRP, var.labels=c("Rheumatoid Arthritis","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$RARTYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Rheumatoid Arthritis","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Glaucoma**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$GLAUYN, vetsa1AllDat$VETSAGRP, var.labels=c("Glaucoma","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$GLAUYN, vetsa2AllDat$VETSAGRP, var.labels=c("Glaucoma","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$GLAUYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Glaucoma","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**PTSD**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$PTSDYN, vetsa1AllDat$VETSAGRP, var.labels=c("PTSD","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$PTSDYN, vetsa2AllDat$VETSAGRP, var.labels=c("PTSD","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$PTSDYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("PTSD","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Migraines**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$MIGRYN, vetsa1AllDat$VETSAGRP, var.labels=c("Migraines","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$MIGRYN, vetsa2AllDat$VETSAGRP, var.labels=c("Migraines","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$MIGRYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Migraines","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Seizures**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$SEIZYN, vetsa1AllDat$VETSAGRP, var.labels=c("Seizures","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$SEIZYN, vetsa2AllDat$VETSAGRP, var.labels=c("Seizures","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$SEIZYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Seizures","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Stroke**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$STROYN, vetsa1AllDat$VETSAGRP, var.labels=c("Stroke","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$STROYN, vetsa2AllDat$VETSAGRP, var.labels=c("Stroke","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$STROYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Stroke","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Alcohol Abuse or Dependency**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$AAADYN, vetsa1AllDat$VETSAGRP, var.labels=c("Alcohol Abuse or Dependency","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$AAADYN, vetsa2AllDat$VETSAGRP, var.labels=c("Alcohol Abuse or Dependency","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$AAADYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Alcohol Abuse or Dependency","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Depression**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$DEPRYN, vetsa1AllDat$VETSAGRP, var.labels=c("Depression","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$DEPRYN, vetsa2AllDat$VETSAGRP, var.labels=c("Depression","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$DEPRYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Depression","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Anxiety**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$ANXDYN, vetsa1AllDat$VETSAGRP, var.labels=c("Anxiety","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$ANXDYN, vetsa2AllDat$VETSAGRP, var.labels=c("Anxiety","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$ANXDYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Anxiety","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Drug Abuse or Dependency**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$DADDYN, vetsa1AllDat$VETSAGRP, var.labels=c("Drug Abuse or Dependency","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$DADDYN, vetsa2AllDat$VETSAGRP, var.labels=c("Drug Abuse or Dependency","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$DADDYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Drug Abuse or Dependency","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Cancer**  
1=Yes, 2=No, 8=Don't Know
`r sjt.xtab(vetsa1AllDat$CANCYN, vetsa1AllDat$VETSAGRP, var.labels=c("Cancer","VETSA 1 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa2AllDat$CANCYN, vetsa2AllDat$VETSAGRP, var.labels=c("Cancer","VETSA 2 Group"),no.output=TRUE)$knitr`  
<br/>
`r sjt.xtab(vetsa1ARAllDat$CANCYN, vetsa1ARAllDat$VETSAGRP, var.labels=c("Cancer","VETSA Group"),no.output=TRUE)$knitr`  
<br/>
<br/>

**Age**  
```{r, echo=F}
# Education
t.test(AGE_IN ~ VETSAGRP, data=vetsa1AllDat)
t.test(AGE_FU1 ~ VETSAGRP, data=vetsa2AllDat)

```
<br/>

**Education**  
```{r, echo=F}
# Education
t.test(TEDALL ~ VETSAGRP, data=vetsa1AllDat)
t.test(TEDALL ~ VETSAGRP, data=vetsa2AllDat)
t.test(TEDALL ~ VETSAGRP, data=vetsa1ARAllDat)
```
<br/>

**AFQT**  
```{r, echo=F}
# AFQT
t.test(afqtpcttran ~ VETSAGRP, data=vetsa1AllDat)
t.test(afqtpcttran ~ VETSAGRP, data=vetsa2AllDat)
t.test(afqtpcttran ~ VETSAGRP, data=vetsa1ARAllDat)
```
<br/>

**Age 20 AFQT**  
```{r, echo=F}
# Age 20 AFQT
t.test(nas201tran ~ VETSAGRP, data=vetsa1AllDat)
t.test(nas201tran ~ VETSAGRP, data=vetsa2AllDat)
t.test(nas201tran ~ VETSAGRP, data=vetsa1ARAllDat)
```
<br/>

**Depression**  
```{r, echo=F}
# Depression
t.test(cesd ~ VETSAGRP, data=vetsa1AllDat)
t.test(cesd ~ VETSAGRP, data=vetsa2AllDat)
t.test(cesd ~ VETSAGRP, data=vetsa1ARAllDat)
```
<br/>

**Income**  
```{r, echo=F}
# Depression
t.test(INCOME ~ VETSAGRP, data=vetsa1AllDat)
t.test(INCOME ~ VETSAGRP, data=vetsa2AllDat)
t.test(INCOME ~ VETSAGRP, data=vetsa1ARAllDat)
```


```{r, include=FALSE}
#Save out datasets used for analysis
write.csv(vetsa1AllDat, "/home/jelman/netshare/K/Projects/PracticeEffects/data/GroupComparisons_V1_V1V2.csv")
write.csv(vetsa2AllDat, "/home/jelman/netshare/K/Projects/PracticeEffects/data/GroupComparisons_V1V2_V2AR.csv")
write.csv(vetsa1ARAllDat, "/home/jelman/netshare/K/Projects/PracticeEffects/data/GroupComparisons_V1_V2AR.csv")
```